One-dimensional Classical Gas in a Harmonic Trap with Repulsive Interaction

### 2017-01-10 Zhiyu.tex
Jan10 PRE format, tex

\begin{comment}
\begin{figure}
\centering
\includegraphics[scale=0.3]{D:/OriginUserfiles/MPI_internship/E_R_fitting.jpg}
-\caption{E-R} This picture shows $E=kR^2$ when energy is large. ($k=N\omega_0^2$)
\end{figure}
\end{comment}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.2]{C:/Users/admin/Desktop/test.png}
\caption{effective potential for two-particle system}
\label{fig:thermalization2}
\end{figure}

>>>>

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/effective_potential.png}
\caption{effective potential for two-particle system}
\label{fig:thermalization2}
\end{figure}
